Under-approximation of reachability through static analysis in multivalued asynchronous networks

### 2013-03-25 main.tex
authors typo
update abstract

\author{Morgan Magnin\thanksref{myemail}}
\address{\towrite{PRES LUNAM + IRCCyN}}

\author{Olivier Roux\thanksref{myemail}}
\address{\towrite{PRES LUNAM + IRCCyN}}

@@

In this paper, we focus on a restriction of the Process Hitting with priorities by considering a class of models equivalent to multivalued networks.
Then, we develop a new refinement for the under-approximation of the static analysis to give accurate results for this set of Process Hitting models.

>>>>

\author{Morgan Magnin}
\address{\towrite{PRES LUNAM + IRCCyN}}

\author{Olivier Roux}
\address{\towrite{PRES LUNAM + IRCCyN}}

@@

In this paper, we focus on a restriction of the Process Hitting with two priorities and a specific behaviour of the components.
We show that this class of Process Hitting models allows to represent any asynchronous networks, either boolean or multivalued.
Then we develop a new refinement for the under-approximation of the static analysis to give accurate results for this set of Process Hitting models.
Thus, our method allows to efficiently under-approximate local reachability properties in asynchronous multivalued networks.
